\section{AI and Jarvis Architecture Review}\label{sec:ai-jarvis}

This section audits the \code{netframe-monitor} / Jarvis AI-operations system as a production
operational system, not as a demo. The central question is whether a language model is ever
permitted to state a conclusion as fact, take an action, or become a command without a
deterministic gate and explicit human approval. The short answer, verified against the code
(E-14), is no: the design is safety-first, and it is one of the signature strengths of this lab.

\subsection{Architecture and data flow}

The system separates a deterministic plane from a model plane, and the deterministic plane is
load-bearing for every safety-critical function.

\begin{itemize}
\item \rh{Collection (no model).} \code{netframe\_monitor.py} runs every 15 minutes via
\code{netframe-run.sh}, SSHing read-only probes across seven nodes with a dedicated
\code{monitor\_key} and writing \code{last\_run.json} plus an append-only \code{history.jsonl}.
It includes end-to-end user-impact probes (\code{LLM\_ROUTER} through NPM, and
\code{LLM\_ROUTER\_CONFORMANCE} reporting config, runtime, and firewall as three independent
dimensions that are never collapsed).
\item \rh{Report paths.} \code{netframe\_interpret.py} (now), \code{netframe\_daily.py},
\code{netframe\_predict.py} (deterministic least-squares forecast), \code{netframe\_monthly.py},
and \code{netframe\_chief.py} (weekly synthesis). Every path imports both \code{netframe\_policy}
and \code{netframe\_evidence} and ends with the same sequence: model prose, then a deterministic
evidence section, then \code{netframe\_policy.enforce()}.
\item \rh{Admission screen.} \code{netframe\_admission.py} vetoes resource-consuming probes on
72B residency, GPU-busy, interactive user, maintenance window, or minimum interval, and fails
closed when GPU state is unknown, so the monitor never becomes the workload it monitors.
\item \rh{Deterministic alerter.} \code{netframe\_alert.py} fires node-down Discord messages
straight from \code{last\_run.json} on UNREACHABLE transitions, independent of Grafana, using
fixed templates (nothing for a model to influence).
\item \rh{Config drift.} \code{netframe\_confdrift.py} fingerprints interfaces, ssh, sysctl, and
env over the read-only path and diffs against a human-blessed baseline.
\item \rh{Interfaces.} \code{netframe\_console.py} serves a read-only HTTP API with no execute
endpoint; both the console and report pages are iptables-locked to localhost plus NPM.
\item \rh{Model routing.} \code{llm\_router.py} defaults to local Ollama \code{qwen2.5:72b},
serves a \code{rag} model over a numpy cosine index, and escalates to \code{claude-opus-4-8}
on an explicit flag, a \code{claude-} model, or local failure.
\item \rh{Audit.} \code{netframe\_audit.py} maintains a hash-chained, tamper-evident, append-only
ledger mirrored to Loki at write time.
\end{itemize}

\subsection{AI-safety control matrix}

{\footnotesize\sansfont
\begin{longtable}{@{}p{0.30\linewidth} p{0.52\linewidth} p{0.12\linewidth}@{}}
\toprule
\rh{Control} & \rh{Implementation (evidence E-14)} & \rh{Verdict}\\
\midrule
\endhead
Single shared evidence engine & \code{netframe\_evidence.py} is called by all six paths; the Findings contract forbids the model stating a confidence; \code{strip\_model\_confidence} removes any residual confidence text on the free-form console path & Strong\\
Provenance and evidence age & Every factor carries provenance; \code{freshness()} with \code{FRESHNESS\_MAX\_S} = 5400s caps confidence at 40 and renders STALE; unverifiable citations contribute zero and trigger a 30 ceiling & Strong\\
Deterministic confidence & \code{evidence\_quality} and \code{confidence} are pure-stdlib floors-plus-ceilings over telemetry; the module states "no model is consulted here"; tightest ceiling wins & Strong\\
Human-gated remediation & \code{netframe\_remediate.py}: 3-item Tier-1 allowlist only, list-form argv (no shell), requires explicit \code{approve} plus confidence >= 95; anything else refuses and prints a manual workflow & Strong\\
Universal policy screening & \code{netframe\_policy.enforce()} is the single gate on every model-to-operator path, including chat; the Discord alerter is deterministic templates with nothing to bypass & Strong\\
Model output never a command & \code{\_guard\_actions} strips shell commands and code fences from chat output and honors only an allowlisted \code{[action:id]} tag; the console, not the model, renders the gated command & Strong\\
Untrusted telemetry & Telemetry wrapped in BEGIN/END UNTRUSTED markers with a data-not-instructions prompt, plus a deterministic injection tripwire (honest caveat: a tripwire for overt imperatives, not a boundary) & Good\\
Model-offline survivability & Collector, alerter, confdrift, admission, forecast tables, and evidence scoring are all no-model; node-down alerts fire before any LLM step & Strong\\
Failed model calls & Every path degrades to a deterministic fallback; \code{policy.enforce} fails LOUD but not closed (emits an UNSCREENED stamp rather than suppressing) & Strong\\
\bottomrule
\end{longtable}}

\subsection{Maturity by function}

{\footnotesize\sansfont
\begin{tabularx}{\linewidth}{@{}p{0.24\linewidth} p{0.22\linewidth} X@{}}
\toprule
\rh{Function} & \rh{Rating} & \rh{Basis}\\
\midrule
Monitoring assistant & Strong / production & Deterministic 15-min collector, dead-man heartbeat, Grafana-independent alerter, locked read-only surfaces\\
Incident analysis & Good & Deterministic blast-radius from a knowledge graph, two-axis evidence and confidence per finding\\
Capacity planning & Solid (deterministic) & Least-squares slope and days-to-90\%; math never delegated to the model\\
Documentation & Strong & Auto now/daily/weekly/monthly reports, hash-chained ledger, unified memory dashboard\\
Change planning & Recommend-only & Chief P0-P3 ranking; \code{propose} emits a manual workflow; confdrift human-bless gate\\
Remediation & Minimal / human-gated & 3-action allowlist, confidence gate, never autonomous (constitution \code{authority\_limits.md})\\
\bottomrule
\end{tabularx}}

\subsection{Code versus documentation}

The \code{jarvis-ai-ops} LaTeX corpus is explicitly propose-and-assess. The code is now ahead of
those assessments on the two biggest historical gaps: the two-axis evidence scoring proposed in
NF-AIOPS-005 is fully implemented, and the tamper-evident audit ledger flagged as open in
JAR-12 is built. Two residual gaps remain and are reflected in the recommendations:

\begin{itemize}
\item \rh{Remediation approval gate (JAR-08, QL-REC13).} Report and chat confidence are now
deterministic, but the Tier-1 execution gate still reads a caller-supplied \code{confidence}
integer rather than the \code{netframe\_evidence} engine. The gate is safe by construction
(allowlist plus explicit approval) but the number is not yet wired to computed evidence.
\item \rh{Config conformance.} \code{confdrift} compares production to a blessed snapshot of
production, not to Git. The specific llm\_router env-drift incident class is now covered by the
separate conformance probe, but a general conform-to-Git target is not yet built.
\end{itemize}

\begin{callout}[title=Assessment]
As a home-lab AI-operations platform this is unusually mature. The trust foundation - single
deterministic evidence engine, universal policy screen, human-gated allowlist remediation,
untrusted-input handling, and full model-offline survivability - is enterprise-grade. Critical
alerting does not depend on any single AI model, and no model output can become an action or a
shell command without a deterministic gate and explicit approval. The remaining lift is the
intelligence layer (evaluation harness, retrieval calibration, Git conformance), not the safety
layer. This directly satisfies the review requirement that deterministic monitoring remain
available if the AI is offline and that remediation cannot occur without approval.
\end{callout}

\subsection{Credentials the AI touches}

Reported by type and location only, values redacted (E-14). \code{ANTHROPIC\_API\_KEY} in
\code{/etc/llm\_router.env} (0600, unset means local-only); \code{DISCORD\_BOT\_TOKEN} and the
operator user id in \code{/etc/netframe-alert.env} (root 0600); the read-only \code{monitor\_key}
used by the collector, confdrift, and the scoped wazuh-restart wrapper; and the restic backup
passphrase file. The restic passphrase is the one single-point risk: if it lives only on Jarvis,
loss of that host makes the encrypted backup unreadable, so it must also live in Vaultwarden.
No hardcoded secrets were found in any source file read.
