\section{Infrastructure Inventory}\label{sec:inventory}

Every entry below is confirmed from live read-only SSH evidence collected 2026-07-23
(E-01 through E-08) unless explicitly flagged as documented-only. Where the live reading
disagrees with a repository document, the live value is treated as canonical and the
discrepancy is carried into the drift register (Section~\ref{sec:drift}).

\subsection{Compute and storage hosts}

The estate is a seven-node Proxmox VE cluster (\code{km-cluster}) plus one standalone
Proxmox host (\code{pve1}). The two Dell R730 servers and the SuperMicro storage node
carry the production research, inference, and storage workloads; the four HP EliteDesk
nodes carry the network edge and core services.

{\footnotesize\sansfont
\begin{longtable}{@{}p{1.6cm}p{2.4cm}p{3.3cm}p{2.2cm}p{1.5cm}p{3.2cm}@{}}
\toprule
\rh{Host} & \rh{Role} & \rh{CPU / RAM} & \rh{GPU} & \rh{PVE} & \rh{Kernel / status} \\
\midrule
\endfirsthead
\toprule
\rh{Host} & \rh{Role} & \rh{CPU / RAM} & \rh{GPU} & \rh{PVE} & \rh{Kernel / status} \\
\midrule
\endhead
\bottomrule
\endfoot
pve1 & Standalone Pi-hole / homepage host (NOT a cluster member) & Mac Mini, 16\,GB & none & 9.1.9 & 7.0.0-3-pve; 142 pending updates; \code{openipmi} failed (no BMC) \\
pve2 & OPNsense host + cluster node & i7-8700, 32\,GB & none & 9.2.3 & 7.0.12-1-pve; reboot-required; excluded from hardening role \\
pve3 & Core services + rke2-cp1 & i7-8700, 48\,GB & none & 9.2.3 & 7.0.12-1-pve; e1000e TSO/GSO-off mitigation persisted \\
pve4 & Grafana stack + rke2-cp2 & i5-7500T, 32\,GB & none & 9.2.3 & 7.0.12-1-pve; sustained load $\sim$5 \\
pve5 & Headscale, Pi-hole2, rke2-cp3, HAOS & i5-7500T, 32\,GB & none & 9.2.3 & 7.0.12-1-pve \\
QuarkyLab & ML / DUNE research / student GPU & 2$\times$ E5-2699 v4 (44c/88t), 512\,GB & 1$\times$ RTX 8000 48\,GB & 9.2.3 & 6.14.11-9-pve (pinned); kernel + full \code{nvidia-*} held \\
Jarvis & LLM inference & 2$\times$ E5-2687W v4, 384\,GB & 2$\times$ RTX 6000 24\,GB & 9.2.3 & 6.14.11-9-pve (pinned); kernel held only (QL-R12) \\
Randy & Storage / PBS / Jellyfin / rke2 storage worker & 2$\times$ E5-2690 v3 (24c/48t), 128\,GB ECC & RX 580 (transcode) & 9.2.3 & 7.0.12-1-pve; docs say 9.1.1 (DR-10) \\
\end{longtable}}

\begin{callout}[title=Live confirmations of contested facts]
\begin{itemize}
\item \textbf{GPU assignment (DR-01):} \code{nvidia-smi} confirms QuarkyLab carries the single
RTX 8000 (46080\,MiB) and Jarvis carries two RTX 6000 (24576\,MiB each), driver 550.163.01.
The review specification's "correction" inverting these is wrong and must not be applied.
\item \textbf{Kernel pins intact:} both GPU nodes run the pinned \code{6.14.11-9-pve}; the pin
protects the NVIDIA 550 stack. Never upgrade the kernel or change \code{GRUB\_DEFAULT} on either
node (QL-REC20).
\item \textbf{Randy PVE version (DR-10):} live \code{pveversion} reports \code{pve-manager/9.2.3},
whereas CLAUDE.md, README, and the fact ledger still state 9.1.1. New drift found by this review.
\item \textbf{Patch lag:} pending-update counts range 63 (Randy) to 142 (pve1); all cluster nodes
report reboot-required (QL-R13).
\end{itemize}
\end{callout}

\subsection{Network devices}

{\footnotesize\sansfont
\begin{tabularx}{\linewidth}{@{}p{2.6cm}p{2.4cm}p{1.8cm}X@{}}
\toprule
\rh{Device} & \rh{Model} & \rh{Mgmt IP} & \rh{Role / status} \\
\midrule
EX3400-48P & Juniper EX3400 & 192.168.10.50 & Core switch, JunOS 23.4R2-S7.4, RSTP root (priority 4096), dual PSU. SSH key auth broken (QL-R16). \code{xe-0/2/3} DOWN - SFP EEPROM speed mismatch (DR-14). \\
USW-24-250W & UniFi & via UDR & Access switch, trunk to \code{ge-0/0/46}. \\
UDR & UniFi Dream Router & 192.168.10.2 & VLAN 1 wireless controller / AP - NOT the WAN edge. \\
EX2300-48P & Juniper EX2300 & - & Lab / CCNA access switch. \\
AP7901 & APC & - & Managed PDU on \code{ge-0/0/38}. \\
\end{tabularx}}

The EX3400 could not be inspected live: SSH refused the offered key (E-22), confirming the
open reconciliation item R-09. Switch state is therefore taken from repository runbooks and
the SNMP feed the dashboard already scrapes, not from a live console pull.

\subsection{Power devices}

Two UPS units protect the estate (live readings in Section~\ref{sec:power}):
Middle Atlantic UPS-OL2200R (UPS-B, servers and shelf) and Tripp Lite SMART1500VA
(UPS-A, switch, UniFi, EliteDesk nodes). Both are online at full charge.

\subsection{Hardware roadmap}

Two hardware changes are in flight and should be tracked as capacity/redundancy items:
Randy RAM expansion 128\,GB $\rightarrow$ 192\,GB (+64\,GB on hand), and a Dell R730xd
being commissioned as a second PBS/backup target and Jellyfin transcode node. The R730xd
directly addresses the single-backup-node gap (QL-R03, QL-REC03) and its power impact is
estimated in Section~\ref{sec:power}.
