\section{Limitations and Confidence}\label{sec:limits}

This was a read-only review conducted in a single working session. Its conclusions
are only as strong as the read-only evidence that supports them, and several areas
could not be examined to the depth a change-authorized or longer engagement would
allow. The limitations below are stated plainly so that the reader can calibrate
each conclusion.

\subsection{Access and method limitations}

\begin{itemize}
  \item \textbf{Read-only ceiling.} No configuration-changing or service-affecting
  command was run, so any finding that would require mutating state to confirm (for
  example, an actual restore test, a failover, or a UPS self-test) is assessed from
  configuration and documentation rather than demonstrated behavior.
  \item \textbf{OPNsense not live-inspected (E-23).} By design, no OPNsense API
  credential was used and VM 100 was not touched. Firewall rules, the running
  version, DHCP reservations, and gateway status therefore rest on the repository
  and the operator's AARs. The version 25.1.12 is documented but not re-verified
  live; confidence in firewall specifics is \textbf{medium}.
  \item \textbf{EX3400 now live-inspected (E-22 / E-25) - limitation lifted.} SSH key
  authentication to the switch is still not configured, but the operator supplied
  password credentials during the review, so config, VLAN membership, spanning-tree
  state, optics, and neighbors were all pulled read-only. Switch facts are now
  \textbf{high} confidence. The residual gap is automation, not visibility: there is
  still no nightly config capture (QL-R16, QL-REC09).
  \item \textbf{Grafana rule load not independently confirmed.} The device-level
  \code{ZfsDeviceFaulted} rule was authored and the new metric was verified live in
  Prometheus, but the reviewer could not independently confirm that Grafana loaded the
  rule: the CT103 exec path repeatedly timed out and the alert API requires
  authentication. The end-to-end proof is operator confirmation that the alert reached
  Discord. The underlying metric is verified; only the rule-load step rests on the
  operator's report.
  \item \textbf{Faulted-drive identity.} Live \code{multipath -ll mpathv} returned
  empty during this session (E-04); the drive's WWN (\code{5000c500631a54fb}) and
  model (Seagate ST4000NM0023) are taken from the prior audit, which is corroborated
  by the live FAULTED state and the NF-INC-2026-07-22 record. Confidence in the
  fault is \textbf{high}; in the exact device identity, \textbf{medium-high}.
  \item \textbf{Binary artifacts not text-scanned.} Roughly 50 committed PDFs
  (concentrated in the assessment repositories) were not decoded for embedded
  secrets. The identity/secrets and IPAM PDFs in the enterprise-assessment repo
  warrant a human eyes-on for sensitivity (E-17).
  \item \textbf{Point-in-time metrics.} Live CPU, memory, UPS load, and job-queue
  readings are instantaneous. UPS runtime in particular is a load-dependent estimate
  and will vary; the imbalance conclusion (QL-R17) is robust, but the exact minutes
  are a snapshot.
  \item \textbf{Prior-assessment age.} The enterprise (E-18) and reliability (E-20)
  assessments are roughly 9 to 10 days old; some of their items have since been
  remediated (for example the GPU-persistence power fix). Their findings are used as
  corroboration and history, reconciled against current state where possible.
\end{itemize}

\subsection{Confidence by major conclusion}

\begin{itemize}
  \item \textbf{High:} cluster quorum and membership; GPU assignment; ZFS pool
  health including the \code{bulk} fault; backup freshness; UPS online state and the
  load imbalance; repository secrets-cleanliness of tracked content; the at-rest
  workstation credential findings.
  \item \textbf{Medium-high:} the faulted device's precise identity; storage
  geometry details on the DS4246; the AI-ops safety controls (read from code, not
  runtime-traced).
  \item \textbf{Medium:} network control-plane specifics (OPNsense and EX3400);
  alert-rule delivery; the true applied state of the Ansible hardening role, which
  is \code{--check}-only and not enforced on nodes (E-24 / DR-12).
\end{itemize}

No unauthorized change was made at any point during this review, and no discovered
credential was used or reproduced in full.
