\section{Monitoring, Logging, and Alerting}\label{sec:monitoring}

\subsection{Stack and topology}

Observability is a Grafana, Prometheus, Loki, InfluxDB, and Scrutiny stack running together in
CT103 on pve4 (\code{192.168.10.183}), live-confirmed (E-06). Alerting uses Grafana Unified
Alerting straight to Discord with no Alertmanager. Two contact points exist: an infrastructure
channel (\code{discord-alerts}) and a UPS channel (\code{discord-ups}). Prometheus was reported
at 15 of 15 targets up (E-15), which means the silent not-scraping failure mode is clean.
Config lives as code in a private repository, which is a genuine operational-maturity strength.

\subsection{Alert inventory}

The following rules were extracted from the provisioning repository (E-15). \code{GAP-} rows are
missing alerts, not deployed ones.

{\footnotesize\sansfont
\begin{longtable}{@{}p{0.24\linewidth} p{0.16\linewidth} p{0.08\linewidth} p{0.24\linewidth} p{0.18\linewidth}@{}}
\toprule
\rh{Alert} & \rh{Source} & \rh{Sev} & \rh{Threshold} & \rh{Disposition}\\
\midrule
\endhead
ClusterNotQuorate & corosync textfile & crit & quorate < 1, 2m & Keep\\
ClusterVotesBelowExpected & corosync textfile & warn & votes deficit > 0, 5m & Keep\\
InstanceDown & node/blackbox & crit & up < 1, 2m & Keep\\
PiholePrimaryDown & blackbox DNS & crit & probe .177 < 1, 2m & Keep\\
PiholeSecondaryDown & blackbox DNS & warn & probe .178 < 1, 2m & Keep\\
ZfsPoolDegraded & zpool textfile & crit & health > 0, 5m & Keep; blind to device faults\\
ZfsDeviceFaulted & zpool textfile & crit & non-ONLINE devices > 0, 5m & \textbf{Added 2026-07-23}\\
GpuTempHigh & nvidia-smi textfile & warn & temp > 87C, 5m & Keep\\
GpuMemoryHigh & nvidia-smi textfile & warn & VRAM used > 90\%, 10m & Keep\\
DiskAlmostFull & node\_filesystem & warn & root > 90\%, 10m & Extend to pools\\
LowMemory & node\_memory & warn & avail < 8\%, 10m & Keep\\
RegistryCertExpiringSoon & blackbox tls & warn & cert < 12h, 15m & Broaden to all certs\\
BackupVerifyReportStale & Randy textfile & warn & age > 26h, 15m & Keep (caught mpathv)\\
BackupVerifyFailing & Randy textfile & warn & pass < 1, 5m & Consider critical\\
AresBackupStale & Randy textfile & warn & age > 26h, 15m & Keep\\
NetframeMonitorStale & Jarvis heartbeat & warn & age > 1h, noData alerting & Keep (dead-man)\\
UPS battery low & PeaNUT & crit & charge < 50, 2m & Keep\\
UPS runtime low & PeaNUT & crit & runtime < 300s, 1m & Keep\\
PrimaryWANDown & pve2 textfile & crit & gateway < 1, 1m & Keep\\
FirewallBlockRateSpike & Loki filterlog & warn & > 500 / 5m & Keep\\
NetworkDeviceConfigChange & Loki syslog & warn & commit > 0 & Keep\\
NetworkSyslogSilent & Loki stream & warn & < 50 / 15m, noData alerting & Keep (dead-man)\\
\midrule
GAP-quorum-guest & (needs pve-exporter) & - & per-guest down & Missing (QL-REC06/07)\\
GAP-pbs-verify-stale & - & - & PBS verify failed/stale & Missing (QL-REC07)\\
GAP-host-auth-failure & - & - & repeated auth failures & Missing (DETECT-01c)\\
GAP-cert-expiry-broad & - & - & any internal/LE cert near expiry & Missing (only registry today)\\
GAP-2nd-channel & - & - & alert egress independent of WAN/Discord & Missing (QL-REC14)\\
\bottomrule
\end{longtable}}

\subsection{Coverage}

{\footnotesize\sansfont
\begin{tabularx}{\linewidth}{@{}p{0.20\linewidth} p{0.10\linewidth} X@{}}
\toprule
\rh{Signal} & \rh{Status} & \rh{Notes}\\
\midrule
Availability & Covered & InstanceDown, Pi-hole probes, PrimaryWANDown, quorum\\
Latency & Partial & OPNsense per-WAN latency on dashboard only; DNS probe is up/down\\
Errors & Partial & Journal errors as a dashboard chip; FirewallBlockRateSpike; no app error-rate rule\\
Saturation & Covered & LowMemory, GpuMemoryHigh; no CPU-saturation rule\\
Capacity & Partial & DiskAlmostFull on root only; pool/non-root capacity not alerted\\
Temperature & Covered & GpuTempHigh; no CPU or ambient temp alert\\
Power & Covered & UPS battery and runtime via PeaNUT\\
Storage health & Covered & ZfsPoolDegraded plus new ZfsDeviceFaulted (device-level, added this review) plus Scrutiny SMART\\
Cert expiry & Narrow & Registry TLS only; other certs not monitored\\
Backup success & Covered & BackupVerify stale/failing, AresBackupStale\\
Auth failures & Gap & No host auth-failure alert rule (dashboard chip only)\\
Config drift & Partial & Hardening-drift chip and NetworkDeviceConfigChange; no host config-drift alert\\
\bottomrule
\end{tabularx}}

\subsection{Blind spots and self-dependency}

\begin{itemize}
\item \rh{Single alert egress (QL-R09, DETECT-01d).} All alerts leave over one Discord webhook
across the WAN. A WAN or Discord outage blinds alerting, and the deterministic node-down message
shares that path. A second out-of-band channel is recommended (QL-REC14).
\item \rh{Co-located stack (QL-R10).} Metrics, logs, and alert evaluation all run in one CT on
one node. Losing that node loses monitoring and stops alert evaluation.
\item \rh{Loki unauthenticated.} \code{auth\_enabled: false} on VLAN 1 makes logs readable and
poisonable by any VLAN 1 host.
\item \rh{SIEM scope (QL-R22).} Wazuh agents run only on the eight hypervisors; guests, OPNsense,
the switch, and endpoints are blind to the SIEM.
\end{itemize}

\begin{callout}[title={The silent-alert lesson, root-caused and closed}]
The degraded \code{bulk} pool was masked for roughly 71 hours, and the condition was ultimately
surfaced by \code{BackupVerifyReportStale} rather than by \code{ZfsPoolDegraded}. This review
determined the cause, and it was \textbf{not} an alert-delivery failure.

The collector \code{zfs-pool-textfile.sh} emitted only \code{node\_zfs\_pool\_health}, derived
from \code{zpool list -o health}. That property returns ONLINE for \code{bulk} because the
raidz2 vdev still holds redundancy, so the metric read 0 (healthy) the entire time. The proof is
unambiguous: \code{max\_over\_time(node\_zfs\_pool\_health\{pool="bulk"\}[7d])} evaluated to
\textbf{0}, so the rule, which fires on \code{> 0}, could never have triggered. No per-device
metric existed anywhere in the stack. A faulted disk inside a still-redundant pool was simply
invisible to alerting (QL-R11).

\textbf{Remediated 2026-07-23.} The collector now also emits
\code{node\_zfs\_pool\_nonhealthy\_devices\{pool\}}, a count of vdev devices not ONLINE, and a
new critical rule \code{ZfsDeviceFaulted} fires on \code{> 0} for 5m to the infra channel. It is
deployed to Randy, QuarkyLab and Jarvis and verified live in Prometheus: \code{bulk} = 1, every
other pool = 0. This rule would have paged on day one. Config-as-code lives in
\code{netframe-monitoring-stack} branch \code{fix/zfs-device-level-alert}.

A second problem surfaced while deploying it: the collector running on all three nodes had
drifted ahead of the repository, carrying an uncommitted \code{node\_zfs\_pool\_capacity\_percent}
metric. Deploying the repository copy unchanged would have silently deleted a live metric. It was
reconciled into the repository first (DR-17). The backup-verify scheduler itself has separately
been moved to a persistent systemd user timer.
\end{callout}

\subsection{What is done well}

Dead-man heartbeats already exist (\code{NetframeMonitorStale}, \code{NetworkSyslogSilent}, both
alerting on noData), a corosync quorum textfile alert has been added, WAN-down detection is wired
from OPNsense dpinger, and the entire configuration is version-controlled. The recommended next
steps are a read-only \code{prometheus-pve-exporter} for guest and quorum metrics (QL-REC06), the
backup-stale, verify-failed, and broad cert-expiry rules (QL-REC07), and the second alert channel
(QL-REC14).
