\documentclass[11pt, letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tabularx}

\definecolor{netblue}{HTML}{5a9bff}
\definecolor{netdark}{HTML}{040c17}

\hypersetup{
    colorlinks=true,
    linkcolor=netblue,
    urlcolor=netblue
}

\pagestyle{fancy}
\fancyhf{}
\rhead{NetFRAME Technologies}
\lhead{Infrastructure Update}
\rfoot{Page \thepage}
\lfoot{June 21, 2026}

\titleformat{\section}{\large\bfseries\color{netblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{NetFRAME Infrastructure Update}}\\[0.5em]
    {\large June 21, 2026}\\[0.3em]
    {\normalsize Randy Commissioning $\cdot$ GPU Swap $\cdot$ DUNE Agent Planning}
\end{center}

\vspace{1em}

%% ─────────────────────────────────────────────────────────
\section{Randy — SuperMicro SYS-2028U-E1CNRT+}

\subsection{Hardware Inventory}

\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Component} & \textbf{Detail} \\
\midrule
Motherboard     & Supermicro X10DRU-i+ \\
Chassis         & SYS-2028U-E1CNRT+ (219U-10) \\
Board Serial    & OM15CS036459 \\
CPUs            & Dual Intel Xeon E5-2690 v4 @ 2.60 GHz \\
RAM             & 128GB ECC DDR4 2133 MHz \\
BIOS            & 3.5 (flashed from 2.0 on 06/21/2026) \\
IPMI            & 192.168.10.22, BMC firmware 03.94, user ADMIN \\
NIC             & Mellanox ConnectX-3 EN 10GbE (MCX312A-XCB7) \\
RAID Card       & LSI MegaRAID (MR RMB L3-25376-00A) + Tecate supercapacitor \\
GPU             & AMD RX 580 8GB DDR5 (installed, awaiting power cable) \\
GPU PWR Headers & 3$\times$ onboard (GPU PWR2/3/4) — SuperMicro proprietary \\
Drive Bays      & 2.5" native bays, 22 caddies total \\
Riser           & RSC-R10W-E8R \\
\bottomrule
\end{tabularx}

\subsection{BIOS Flash — Completed \checkmark}

\textbf{Method:} UEFI Shell via IKVM console (IPMI web UI at 192.168.10.22)

\begin{enumerate}[leftmargin=*, nosep]
    \item Downloaded \texttt{X10DRU2.427.zip} from Supermicro support portal
    \item Created FAT32 UEFI bootable USB on Ares (\texttt{/dev/sda}) via \texttt{parted} + \texttt{mkfs.fat}
    \item Copied UEFI folder contents to \texttt{/EFI/BOOT/} on USB; added \texttt{BOOTX64.EFI}
    \item Fixed broken Java KVM via IKVM Reset (Maintenance $\rightarrow$ IKVM Reset in IPMI)
    \item Booted Randy to UEFI Built-in EFI Shell via F11 boot menu
    \item Navigated: \texttt{fs0:} $\rightarrow$ \texttt{cd EFI\textbackslash BOOT} $\rightarrow$ \texttt{flash.nsh X10DRU2.427}
    \item Two-stage flash: FDT difference detected $\rightarrow$ reboot $\rightarrow$ \texttt{STARTUP.NSH} auto-resumed
    \item \textbf{Result:} BIOS 3.5, ME Entire Image update success
\end{enumerate}

\textit{Key lesson: Supermicro BIOS jumps with different FDT require two boot cycles. First run creates STARTUP.NSH and reboots. Boot back to EFI Shell and let STARTUP.NSH run automatically without pressing ESC.}

\subsection{Parts Ordered — June 21, 2026}

\begin{tabularx}{\textwidth}{llXr}
\toprule
\textbf{Part} & \textbf{Part Number} & \textbf{Purpose} & \textbf{Qty} \\
\midrule
Dell GPU power cable    & N08NH              & Aux power for QuarkyLab dual RTX 6000 & 2 \\
SuperMicro GPU cable    & CBL-PWEX-0665      & 8-pin CPU $\rightarrow$ 8-pin PCIe for RX 580 in Randy & 1 \\
SuperMicro drive caddy  & MCP-220-00075-0B   & 2.5" native caddies for Randy & 2 \\
\bottomrule
\end{tabularx}

\subsection{Randy's Role in Cluster}

Randy is the \textbf{infrastructure backbone} — not a compute node.

\textbf{Services (priority order):}
\begin{enumerate}[leftmargin=*, nosep]
    \item \textbf{Proxmox Backup Server (PBS)} — critical; cluster currently has no backup
    \item \textbf{NFS/ZFS storage} — serves DS4246 JBOD + internal bays to cluster via NFS
    \item \textbf{Jellyfin} — media server; RX 580 handles transcoding via AMD ROCm
    \item \textbf{Prometheus + Grafana + Loki} — migrate from management G4 EliteDesk
    \item \textbf{Scrutiny} — drive health monitoring for 22+ drives
    \item \textbf{MinIO} — S3-compatible object storage for the researcher's datasets
    \item \textbf{Vaultwarden} — password manager (current node TBD)
\end{enumerate}

\textbf{Randy does NOT run:} ML/LLM workloads, Ollama inference, or GPU compute. The RX 580 is for display output and media transcoding only.

\subsection{Pending Before Proxmox Install}

\begin{itemize}[leftmargin=*, nosep]
    \item[$\square$] CBL-PWEX-0665 arrives $\rightarrow$ power RX 580
    \item[$\square$] Confirm video output via RX 580 HDMI $\rightarrow$ KVM drawer
    \item[$\square$] Install Proxmox via external USB (not internal thumb drive)
    \item[$\square$] Determine LSI MegaRAID fate (flash to IT mode vs retain for RAID)
    \item[$\square$] Add Randy to Proxmox cluster
\end{itemize}

%% ─────────────────────────────────────────────────────────
\section{GPU Swap Decision}

\subsection{New GPU Configuration}

\begin{tabularx}{\textwidth}{llllX}
\toprule
\textbf{Server} & \textbf{GPU} & \textbf{VRAM} & \textbf{CUDA} & \textbf{Role} \\
\midrule
QuarkyLab & RTX 8000 (from Jarvis)      & 48GB       & Yes & DUNE research agent \\
Jarvis    & 2$\times$ RTX 6000 (from QuarkyLab) & 48GB total & Yes & LLM inference/Ollama \\
Randy     & RX 580                      & 8GB        & No (ROCm) & Display + transcoding \\
\bottomrule
\end{tabularx}

\subsection{Rationale}

\textbf{QuarkyLab gets RTX 8000:} the researcher's DUNE RAG agent needs maximum single-GPU VRAM. 48GB holds a large code model and embedding model simultaneously without splitting. Single GPU means cleaner inference with no PCIe overhead.

\textbf{Jarvis gets dual RTX 6000:} LLM inference workloads are bursty, not sustained. Ollama handles multi-GPU natively. 48GB aggregate VRAM matches the RTX 8000. PCIe overhead is acceptable for the llm\_router query routing use case.

\textbf{NVLink:} Not required for either server. the researcher's workload is inference and RAG retrieval, not distributed training. No unified VRAM pool is needed.

%% ─────────────────────────────────────────────────────────
\section{the researcher's DUNE Agent Project}

\subsection{Overview}
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Goal:} RAG agent over the DUNE experiment codebase
    \item \textbf{Purpose:} Help new scientists understand the full codebase during onboarding at SURF (South Dakota)
    \item \textbf{Host:} QuarkyLab (after RTX 8000 swap)
    \item \textbf{Claude Project:} ``DUNE Agent'' (created 06/21/2026)
\end{itemize}

\subsection{Architecture}
\begin{itemize}[leftmargin=*, nosep]
    \item RAG pipeline (inference workload, not training)
    \item Embedding model dedicated to RTX 8000 GPU allocation
    \item Inference model on RTX 8000 (48GB accommodates large code model)
    \item Suggested models: Qwen2.5-Coder 32B unquantized or 72B Q4\_K\_M
    \item Vector store: ChromaDB or Qdrant (TBD)
\end{itemize}

%% ─────────────────────────────────────────────────────────
\section{Sandbox / Lab Node}

\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Hardware:} Spare HP EliteDesk G4 (unused, in rack)
    \item \textbf{Status:} Standalone — do NOT add to Proxmox cluster
    \item \textbf{Purpose:} Safe learning environment; CCNA lab; service testing before Randy deployment
    \item \textbf{Tools:} GNS3, EVE-NG, k3s (future)
    \item \textbf{Network:} VLAN 70 (lab), IP range \texttt{192.168.70.x}
    \item \textbf{Hostname:} TBD
\end{itemize}

%% ─────────────────────────────────────────────────────────
\section{Claude Projects Created}

\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Project} & \textbf{Scope} \\
\midrule
NetFRAME --- LLM Infrastructure & Jarvis, Ollama, llm\_router, GPU swap \\
DUNE Agent --- the researcher          & RAG pipeline, codebase ingestion, QuarkyLab ML env \\
\bottomrule
\end{tabularx}

%% ─────────────────────────────────────────────────────────
\section{Full Cluster GPU Inventory}

\begin{tabularx}{\textwidth}{lllllX}
\toprule
\textbf{Server} & \textbf{GPU} & \textbf{VRAM} & \textbf{CUDA} & \textbf{ROCm} & \textbf{Primary Use} \\
\midrule
QuarkyLab & RTX 8000      & 48GB       & Yes & No  & ML / DUNE research \\
Jarvis    & 2$\times$ RTX 6000 & 48GB total & Yes & No  & LLM inference (Ollama) \\
Randy     & RX 580        & 8GB        & No  & Yes & Display + Jellyfin transcode \\
\bottomrule
\end{tabularx}

Every node in the cluster now has a GPU. This enables distributed inference routing across all GPU nodes via \texttt{llm\_router.py} and provides full cluster-wide redundancy for GPU workloads.

\end{document}
